---
title: "Cars Model API"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = FALSE)

knitr::read_chunk("plumber.R")
knitr::read_chunk("cars-model.R")
```

This API demonstrates how to take a machine learning model trained in R and expose it via REST API endpoints using the `plumber` package. In this example, a simple linear model is built on top of the `mtcars` dataset.

```{r cars-model}
```

This code creates the cars model and saves it as an `.rds` file. The [`here`](https://github.com/r-lib/here) package is used to provide help with file paths.

Once the model has been trained and saved, a series of API endpoints can be built around the model. These endpoints are defined in [`plumber.R`](plumber.R) and explained in detail here.

## API Setup
```{r api-setup}
```

This initial setup loads the `plumber` package, loads the saved model, and provides some additional API details (Title and Description). Note that the `cars_model` object is loaded into the global environment here, and is then made available to any filters and endpoints that are subsequently defined. We could also load the model inside the actual `/predict` endpoint function that utilizes the model. However, this would mean that every time the `/predict` endpoint was called, the model would first be loaded before it could be used, rather than being immediately available.

## Filters
[Filters](https://www.rplumber.io/docs/routing-and-input.html#filters) are used by Plumber to perform some action on an incoming request and then forward the request along to the next stop on the router. This API uses a filter to log information about incoming requests, as described in the [Plumber docs](https://www.rplumber.io/docs/routing-and-input.html#forward-to-another-handler).

```{r filter-logger}
```

## Endpoints
This API anticipates that users submit JSON data via a POST request. In Plumber, data submitted with a POST request can be accessed via `req$postBody`. In this endpoint, submitted data is first checked to see if it is valid JSON. If valid JSON is found, the data is converted into a `data.frame` and then the [model](cars-model.R) is used to form predictions based on that data. These predicted values are returned to the client as a JSON object.

```{r post-data}
```
